Data Cleaning logbook

### 2018-04-03 docs/data_cleaning_logbook.Rmd
updated logbook

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(abundancia > 0) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

```{r}
conapesca <- readRDS(here::here("raw_data","conapesca.rds")) %>% 
  filter(UnidadEconomica %in% c("Scpp cozumel scl",
                                "Scpp jose maria azcorra scl",
                                "Scpp buzos y pescadores de la baja california scl")) %>% 
  filter(NombreComun %in% c("Langosta roja ent. fca.", "Langosta ent. fca.")) %>%
  group_by(UnidadEconomica, Ano, NombreComun) %>%
  summarize(PesoDesembarcado = sum(PesoDesembarcado), 
            PesoVivo = sum(PesoVivo),
            Valor = sum(Valor)) %>%
  filter(!(UnidadEconomica == "Scpp buzos y pescadores de la baja california scl" & NombreComun == "Langosta ent. fca.")) %>% 
  left_join(cpi, by = "Ano") %>% 
  mutate(Valor = Valor * (CPI / cpi_2014))
```

>>>>

```{r}
invert <- read.csv(here::here("raw_data", "invert_data.csv"), strip.white = T, stringsAsFactors = F) %>% 
  janitor::clean_names() %>% 
  filter(comunidad %in% c("Isla Natividad", "Maria Elena", "Punta Herrero")) %>% 
  filter(!is.na(rc),
         rc %in% c("La Plana / Las Cuevas - La Dulce / Babencho",
                   "Cabezo - Cabezo (Control)",
                   "Manchon - Manchon (Control)",
                   "El Faro - El Faro (Control)")) %>% 
  filter(!(rc %in% c("El Faro - El Faro (Control)") & ano == 2012)) %>% 
  filter(between(abundancia, 0, 100)) %>% 
  group_by(comunidad, ano, rc, sitio, zona, transecto, generoespecie) %>% 
  summarize(abundancia = sum(abundancia)) %>% 
  ungroup() %>% 
  mutate(year = case_when(comunidad == "Isla Natividad" ~ ano - 2006,
                         comunidad == "Maria Elena" ~ ano - 2012,
                         TRUE ~ ano - 2013)) %>% 
  select(comunidad, ano, year, rc, sitio, zona, transecto, generoespecie, abundancia) %>% 
  arrange()
```

@@

```{r}
cooperatives_t <- c("Scpp cozumel scl",
                    "Scpp jose maria azcorra scl",
                    "Scpp buzos y pescadores de la baja california scl")

cooperatives_c <- c("Scpp langosteros del caribe scl",
                    "Scpp vigia chico scl",
                    "Scpp pesc nacionales de abulon sc de rl",
                    "Scpp la purisima scl",
                    "Scpp bahia tortugas scl")

cooperatives <- c(cooperatives_t, cooperatives_c)
```

```{r}
L_conapesca <- tibble(UnidadEconomica = c("buzos y pescadores de la baja california",
                                          "bahia tortugas",
                                          "pesc nacionales de abulon",
                                          "la purisima",
                                          "cozumel",
                                          "jose maria azcorra",
                                          "vigia chico",
                                          "langosteros del caribe"),
                      Comunidad = c("Isla Natividad",
                                    NA, NA, NA, 
                                    "Maria Elena",
                                    "Punta Herrero",
                                    NA, NA),
                      Zona = c("PN", "PN", "PN", "PN", "MC", "MC", "MC", "MC"),
                      Start = c(2006, 2006, 2006, 2006, 2012, 2013, 2012, 2012))
```

```{r}
conapesca <- readRDS(here::here("raw_data","conapesca.rds")) %>% 
  mutate(UnidadEconomica = as.character(UnidadEconomica)) %>% 
  mutate(UnidadEconomica = ifelse(UnidadEconomica == "Scpp bahia tortugas s.c de r.l", 
                                  "Scpp bahia tortugas scl",
                                  UnidadEconomica)) %>% 
  filter(UnidadEconomica %in% cooperatives) %>%
  filter(NombreComun %in% c("Langosta roja ent. fca.", "Langosta ent. fca.")) %>%
  group_by(UnidadEconomica, Ano, NombreComun) %>%
  summarize(PesoDesembarcado = sum(PesoDesembarcado), 
            PesoVivo = sum(PesoVivo),
            Valor = sum(Valor)) %>%
  ungroup() %>% 
  filter(!(UnidadEconomica == "Scpp buzos y pescadores de la baja california scl" & NombreComun == "Langosta ent. fca.")) %>% 
  left_join(cpi, by = "Ano") %>% 
  mutate(Valor = Valor * (CPI / cpi_2014),
         Group = case_when(UnidadEconomica %in% cooperatives_t ~ "Treated",
                           TRUE ~ "Control"),
         UnidadEconomica = gsub(pattern = "Scpp ", replacement = "", x = UnidadEconomica),
         UnidadEconomica = gsub(pattern = " scl", replacement = "", x = UnidadEconomica),
         UnidadEconomica = gsub(pattern = " s.c de r.l", replacement = "", x = UnidadEconomica),
         UnidadEconomica = gsub(pattern = " sc de rl", replacement = "", x = UnidadEconomica)) %>% 
  left_join(L_conapesca, by = "UnidadEconomica") %>% 
  mutate(Post = ifelse(Ano <= Start, 0, 1),
         years_centered = Ano - Start) %>% 
  select(Zona, Grupo = Group, Comunidad, UnidadEconomica, Ano, Post, years_centered, NombreComun, PesoVivo, PesoDesembarcado, Valor, CPI) %>% 
  janitor::clean_names()
```
